---

title: "Assume concrete strength"
subtitle: "DATA2002 Presentation"
author: "Lab06-early06"
date: "2021"
output:
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false # disable slide transitions by scrolling
---

## Background

<font face = 'Times New Roman', font size = 5.5>Concrete is a common man-made material, it is widely used in building structures, roads and bridges, etc.</font>

<font face = 'Times New Roman', font size = 5.5>The ratio of these components can be varied within a wide range, which will affect the concrete compressive strength.</font>


<font face = 'Times New Roman', font size = 5.5>These include:</font>
+ **Cement**

+ **Blast Furnace Slag**

+ **Fly Ash**

+ **Superplasticizer**

+ **Coarse Aggregate**

+ **Fine Aggregate**

+ **Water**

---

## Introduction



###  Aim

<font face = 'Times New Roman', font size = 5.5><b>Predict the relationship between the compressive strength and composition of concrete.</b></font>



###  Method
<font face = 'Times New Roman', font size = 5.5><b>Multiple Linear Regression</b></font>:<font face = 'Times New Roman', font size = 5.5> Forward and backward step wise variable selection using Akaike information criterion  (AIC).</font>
 
---

## Dataset

```{r, load_refs, echo=FALSE, cache=FALSE, message=FALSE}
#install.packages("RefManageR")

library(RefManageR)

library(tidyverse)
#install.packages("GGally")
library(GGally)

#install.packages("ggfortify")
library(ggfortify)

library(caret)
library(knitr)
library(readxl)
 
library(usethis)
 #加了个这个
 
knitr::opts_chunk$set(echo = FALSE)
```


```{r,results='hide'}
#import data and rename attributes
concrete =readxl::read_xls("/Users/fatx/Desktop/Concrete_Data.xls")
concrete
names(concrete)[1:9] <-c("cement","blast_furnace_slag","fly_ash","water","superplasticizer","coarse_aggregate","fine_aggregate","age","compressive_strength") 
names(concrete)
str(concrete)

```

-  <font face = 'Times New Roman', font size = 5.5>The data is valid, consistent, original, complete and legible.</font>

   https://archive.ics.uci.edu/ml/datasets/Concrete+Compressive+Strength
   

-  <font face = 'Times New Roman', font size = 5.5>This data set has 1030 samples, 9 variables. It is subdivided into 8 quantitative input variables and 1 quantitative output variable.</font>



-  <font face = 'Times New Roman', font size = 5.5>This dataset was collected in 2007 and it is dated.</font>



- <font face = 'Times New Roman', font size = 5.5>First 6 rows of data shown below:</font>



```{r}
knitr::kable(head(concrete),
             col.names =
               c("cement","blast_furnace_slag","fly_ash","water","superplasticizer","coarse_aggregate","fine_aggregate","age","compressive_strength"))
```


```{r, results='hide'}
summary(concrete$compressive_strength)
#avg>mid 分布是右偏的，用直方图证实了这一点？？？？？？
hist(concrete$compressive_strength)
```

---

##Question

<br>
###How can we predict the concrete compressive strength?

</br>

<font face = 'Times New Roman', font size = 5.6>We want to  predict the concrete compressive strength in the future when we have known the amount of each ingredient through our model.</font>

---

## Data Analysis
### Assumptions


-  Linearity - the relationship between the compressive strength of concrete and components as well as age is linear.
-  Independence - all the observations are independent of each other.

-  Homoskedasticity - the errors have constant variance for all.

-  Normality - the errors are distributed normally.


---
### Data Overview

说些什么,图作用

```{r, message=FALSE}
GGally::ggpairs(concrete) + theme_bw()

```



---
### Data Explore

#### Perform a multiple regression of compressive strength of concrete on the other variables using full model.

We firstly overview the relationship between each variable.
Then we put every variables in the dataset into our model.

```{r, message=FALSE}
#在这里不知道是否需要一个boxplot 去check for gross outliers
#boxplot(scale(concrete)) 如果需要可能是这样 但是x轴的坐标需要重新命名。

#Full model
concrete_full_lm = lm(compressive_strength ~ ., concrete)

round(summary(concrete_full_lm)$coef, 3)

car::vif(concrete_full_lm)

```


Dropping values using an information criterion，doing backward selection.
We use step() function to remove the least informative variables to fit our model.

```{r}

#backward
concrete_step_back =  step(concrete_full_lm, direction = "backward", trace = F)

#check backward
summary(concrete_step_back)

```


---

### Data Explore


#### Perform a multiple regression of compressive strength of concrete on the other variables using null model.

```{r, message=FALSE}

#NUll model
concrete_null_lm = lm(compressive_strength ~ 1, concrete)

```

Dropping values using an information criterion，doing forwards selection.
We use step() function to add the most informative variables to fit our model. 

```{r}

#forward
concrete_step_forward = step(concrete_null_lm, scope = list(lower = concrete_null_lm, upper = concrete_full_lm), direction = "forward",trace = F)#大家可以改成T 看它的过程。
summary(concrete_step_forward)
#或concrete_step_forward
```

Obviously, the two models are different,  we need to choose the one which is fitter.


---
### Models performance

#### In sample
```{r}
sjPlot::tab_model(
concrete_step_forward, concrete_step_back,
show.ci = FALSE,
show.aic = TRUE,
dv.labels = c("Forward model"
,"Backward model"))
```

For this compare, the AIC of forward model is little smaller than backward model, forward model could be little better.

---

#### Out of sample
```{r}
library(caret)
set.seed(7777)
cv_F = train(
compressive_strength ~ cement + superplasticizer + 
    age + blast_furnace_slag + water + fly_ash, concrete,
method = "lm",
trControl = trainControl(
method = "cv", number = 10,
verboseIter = FALSE))
cv_F

cv_B = train(
compressive_strength ~ cement + blast_furnace_slag + 
    fly_ash + water + superplasticizer + coarse_aggregate + fine_aggregate + 
    age, concrete,
method = "lm",
trControl = trainControl(
method = "cv", number = 10,
verboseIter = FALSE))
cv_B
```
We do the CV estimation, and there are little differences between two models. therefore, we could choose the model which need less information.
---

### Data Explore


#### The fitted model for the model selected.

we choose forward model as our fitted model:

$$\widehat Strength = 29.03 + 0.11 cement + 0.24 superplasticizer + 0.11 age + 0.09 blast furnace slag  -0.22 water + 0.07 fly ash$$
We can see that the strength is affected more by superplasticizer and water have a negative effect to the strength.

---

### Assumptions Checking

- Independence: Each observation is independent and cannot affect each other. So the independence of data can be satisfied.

```{r}
library(ggfortify)
# plts to check assumptions
autoplot(concrete_step_forward, which = 1:2) + theme_bw()

```

- Linearity: there’s no obvious pattern in the residual vs fitted values plot, so the assumption is satisfied.

- Homoskedasticity: the residuals don’t appear to be fanning out or changing their variability over the range of the fitted values so the assumption is satisfied

- Normality: in the QQ plot, the points are reasonably close to the diagonal line. The normality assumption is approximately satisfied.

---

### Reference
xxx
